\mytitle

### 2015-08-05 MSc_diss.tex
Updates in discussion and conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % epsilon noANs allANs diff 250 ppt 100 ppb
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_epsilon_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilon_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilondiff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production efficiency (or $\epsilon$, molecules of $O_3$ per carbon bond, color) as a function of $VOC$ (ppbC) and $NO_x$ (250ppt - 100 ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:epsilon250ppt100ppb}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % epsilon noANs allANs diff 5 ppt 100 ppb
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_epsilon_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilon_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilondiff_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production efficiency (or $\epsilon$, molecules of $O_3$ per carbon bond, color) as a function of $VOC$ (ppbC) and $NO_x$ (5 ppt - 100 ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:epsilon5ppt100ppb}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discuss}
Use CRI.
Future plans and possible improvements in the model.

The experimental results presented in the previous section provide an opportunity to speculate about the behaviour of our simple model of alkyl nitrate production and loss with time in comparison with the observational data.

\section{Conclusion} \label{sec:conclusion}
\bibliography{diss_refs}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % epsilon noANs allANs diff 250 ppt 100 ppb
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_epsilon_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilon_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilondiff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production efficiency (or $\epsilon$, molecules of $O_3$ per carbon bond, color) as a function of $VOC$ (ppbC) and $NO_x$ (250ppt - 100 ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:epsilon250ppt100ppb}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % epsilon noANs allANs diff 5 ppt 100 ppb
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_epsilon_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilon_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_epsilondiff_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production efficiency (or $\epsilon$, molecules of $O_3$ per carbon bond, color) as a function of $VOC$ (ppbC) and $NO_x$ (5 ppt - 100 ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:epsilon5ppt100ppb}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discuss}
The experimental results presented in the previous section provide an opportunity to speculate about the behaviour of our simple chemistry box conceptual model and its sensitivity to alkyl nitrate production and loss.

This research has limitations link with the disadvantages of the model, not enough experiments.

Due to obvious limitations

Future plans include illumination of all weaknesses from our model, particularly adding other sinks for $NO_x$ into the chemical mechanism.

Probably it is reasonable to conduct a similar kind of research using the Common Representative Mechanism (CRI) which includes representation of alkyl nitrates and is traceable to the MCM.

Future plans and possible improvements in the model.

\subsubsection*{Future research}
A greater depth of information may have been obtained by conducting more experiments.
Another possible improvement to the study could have been

\section{Conclusion} \label{sec:conclusion}
The present study provides an assessment of of

The present study is purely theoretical, investigates the impact of alkyl nitrates on tropospheric ozone production.
We examine the sensitivity of the modelled ozone production to the alkyl nitrate chemistry.

The research hopes to contribute to the atmospheric chemistry research b

We hope that our results concerning the sensitivity of ozone calculations to alkyl nitrate chemistry will be interesting to other researches, as well as the carbon bond efficiency calculations.

\bibliography{diss_refs}
